\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-26 doc/paper.tex
Fixes #142.

		\item [!1] \textbf{Do not make judgments about good and bad design.} Though
		users may certainly approach the tool with the intention of exploring particular
		formulae, \toolname will not prioritize any on metrics of good or bad
		practice.

		\item [2] \textbf{Emphasize the quantitative patterns in formula
			construction.} \toolname should address the questions of how often the
		spreadsheet programmers used a certain function and where they used it. To do
		this, it must show metrics, such as frequency of use and depth of
		function nesting, of the dataset it conveys.

@@

		\item [3] \textbf{Promote a qualitative understanding of the patterns.}
		\toolname should supplement its observations with concrete instances of
		relevant formulae from the corpus. Ideally, it should even direct users to the
		exact cell in the spreadsheets where the formula was used, contextualizing the
		functions.

		\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname tries
		to foster understanding by linking pattern to example, it should not provide a
		precise description of what a complex formula accomplishes. The tool's user
		must infer this on their own.

>>>>

		\item [!1] \textbf{Do not make judgments about good and bad design.} Though
		users may certainly approach the tool with the intention of exploring particular
		formulae, a formula visualization tool will not prioritize any on metrics of good or bad
		practice.

		\item [2] \textbf{Emphasize the quantitative patterns in formula
			construction.} The tool should address the questions of how often the
		spreadsheet programmers used a certain function and where they used it. To do
		this, it must show metrics, such as frequency of use and depth of
		function nesting, of the dataset it conveys.

@@

		\item [3] \textbf{Promote a qualitative understanding of the patterns.}
		The tool should supplement its observations with concrete instances of
		relevant formulae from the corpus. Ideally, it should even direct users to the
		exact cell in the spreadsheets where the formula was used, contextualizing the
		functions.

		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool will
		to foster understanding by linking pattern to example, it should not provide a
		precise description of what a complex formula accomplishes. The tool's user
		must infer this on their own.
